Palomar 5 Gaps

### 2024-09-27 paper/main.tex
more edits

    To understand how the impacted particle is perturbed, one needs to compute its change in momentum, which is determined by integrating the force acting on the particle over the duration of the interaction. A useful approximation for this change in momentum is the force at the closest approach multiplied by an estimate of the interaction time:
    \begin{equation} 
      \Delta p \approx \text{Force} \times \text{interaction time} = \frac{GMm}{b^2} \times \frac{b}{v} = \frac{GM}{bv}, 
      \end{equation} \label{eq:change_in_momentum}
    where $M$ is the mass of the perturber, $m$ is the mass of the particle, $b$ is the impact parameter, $v$ is the relative velocity of the perturber with respect to the particle, and $G$ is the gravitational constant.

@@

  We then transformed the stream to tail coordinates for the both the \texttt{vanilla} and \texttt{full} simulations in Fig.~\ref{fig:profiles}. As described in section~\ref{sec:gap_detection}, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. Notice the \textit{Tiny Gap} labeled in the middle plot. This signal is not present in the 1D profile since it is too small in size and at an oblique angle, thus is lost when marginalizing. This process was followed for all 50 simulations to identify possible gaps. We find that small gaps are identifiable by eye rather well, where the 1D profiles aid in finding subtle yet extended underdensities. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}. The profile method was useful in identifying the subtle underdense gaps of Samplings: 000, 002, 006, 024, 028, 029, 030, 044, \& 048.

>>>>

    To understand how the impacted particle is perturbed, one needs to compute its change in momentum, which is determined by integrating the force acting on the particle over the duration of the interaction. A useful approximation for this change in momentum is the force at the closest approach multiplied by an estimate of the interaction time:
    \begin{equation} 
      \Delta p \approx \text{Force} \times \text{interaction time} = \frac{GMm}{b^2} \times 2\frac{b}{v} = 2\frac{GM}{bv}, 
      \end{equation} \label{eq:change_in_momentum}
    where $M$ is the mass of the perturber, $m$ is the mass of the particle, $b$ is the impact parameter, $v$ is the relative velocity of the perturber with respect to the particle, and $G$ is the gravitational constant.

@@

  We then transformed the stream to tail coordinates for the both the \texttt{vanilla} and \texttt{full} simulations in Fig.~\ref{fig:profiles}. As described in section~\ref{sec:gap_detection}, we locate regions on the stream where the full simulations are significantly less dense than the vanilla simulations. Notice the \textit{Tiny Gap} labeled in the middle plot. This signal is not present in the 1D profile since it is too small in size and at an oblique angle, thus is lost when marginalizing. This process was followed for all 50 simulations to identify possible gaps. We find that small gaps are identifiable by eye rather well in the 2D density maps, where the 1D profiles aid in finding subtle yet extended underdensities. All simulations and labeled gaps are presented in the Appendix~\ref{appendix:gallery_of_gaps}. The profile method was useful in identifying the subtle underdense gaps of Samplings: 000, 002, 006, 024, 028, 029, 030, 044, \& 048.
